Dependently Typed Languages in Statix

### 2023-04-20 pres-thesis/presentation.tex
More work

\begin{frame}[fragile]{Type Checking: Requires Evaluation}
	\begin{figure}
		\includegraphics[width=0.9\linewidth]{screenshot001}
	\end{figure}

@@

>>>>

\begin{frame}[fragile]{Type Checking: Requires Evaluation}
	\begin{figure}
		\includegraphics[width=0.9\linewidth]{screenshot001}
	\end{figure}
\end{frame}

\begin{frame}[fragile]{Type Checking: Variable Capturing}
	todo
\end{frame}

\begin{frame}{Comparison with Haskell}
	\begin{block}{Type checking}
		\texttt{data EnvEntry = NType Expr | NSubst SExpr
			\\type Env = [EnvEntry]
			\\type SExpr = (Env , Expr)
			\\tc :: SExpr -> Either String Expr}
	\end{block}

	\begin{block}{Differences}
		\begin{itemize}
			\item Distribution of definitions over files
			\item De Bruijn Indices vs Names
			\item Inference built-in to Statix
		\end{itemize}
	\end{block}
\end{frame}

\begin{frame}{Term Inference}
	\begin{example}\texttt{let id = ($\backslash$T : Type. $\backslash$x: T. x);
	\\id \_ true}
	\end{example}
	\begin{block}{How it works}
		\begin{itemize}
			\item When we encounter \texttt{expectBetaEq(e1, e2)} and \texttt{e1} or \texttt{e2} is free, we can infer it!
			\item But in Statix we can't query whether variables are free.
			\item Solution: Wrap each free constructor in \texttt{Infer}.
		\end{itemize}
	\end{block}
\end{frame}

\begin{frame}{Term Inference: Equational Unification}
	\begin{itemize}
		\item We can declare two terms to be equal if they satisfy a certain relation (such as beta equality)
		\item We do this using \emph{reduction rules}, such as:
		\begin{exampleblock}{Example of a rewrite rule}
			($\backslash$ x : T. b) a => b[x := a]
		\end{exampleblock}
	\end{itemize}
\end{frame}

\begin{frame}{Comparison with LambdaPi}
	\begin{itemize}
		\item A \emph{logical framework} in which you can embed other programming languages
		\item Supports rewrite rules
		\item Cannot define \emph{Let} because of limitations of LambdaP
	\end{itemize}
\end{frame}

\begin{frame}{Comparison with LambdaPi: Example}

@@

\begin{frame}{Inductive Data Types}
	todo
\end{frame}

\begin{frame}{Interpreter \& Compiler}
	todo
\end{frame}
